---
title: "Getting started with CGLBM"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with CGLBM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

`CGLBM` co-clusters matrix rows and columns while using exact values and
censoring intervals in one reported-data likelihood.

```{r}
library(CGLBM)

z0 <- rep(1:2, each = 4)
w0 <- rep(1:2, each = 4)
mu0 <- matrix(c(-2, 0.5, 0.5, 2.5), 2, 2)
y <- matrix(0, 8, 8)
for (i in seq_len(8)) for (j in seq_len(8)) {
  y[i, j] <- mu0[z0[i], w0[j]] + 0.02 * (i - j)
}

reported <- apply_detection_limits(
  y,
  lower_limit = -2,
  upper_limit = 2.5
)
reported
```

Fit one model with a fixed start. The `S` argument controls the block variance
structure and `P` controls whether row and column class proportions are free or
equal.

```{r}
fit <- censored_lbm(
  reported,
  g = 2,
  m = 2,
  algorithm = "HH",
  S = "Skl",
  P = "free",
  n_starts = 1,
  starts = list(list(z = z0, w = w0)),
  max_start_attempts = 1,
  max_iter = 50,
  seed = 1
)
fit
predict(fit, type = "labels")
summary(fit)
```

The summary reports fitted block means and variances, plug-in standard errors,
effective observed block weights, report counts, and information-equivalent
sample sizes.
