---
title: "Reporting design and block-mean information"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reporting design and block-mean information}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

Fisher-information summaries use the fixed reporting rule, not only the
realized report status. `apply_detection_limits()` retains the complete lower
and upper limits, including at cells that happened to be reported exactly.

```{r}
library(CGLBM)

y <- matrix(c(-2, -0.5, 0.5, 2, -1.5, 0, 1, 2.5), nrow = 4)
reported <- apply_detection_limits(y, lower_limit = -1, upper_limit = 2)
reported$metadata$reporting_design

fit <- censored_lbm(
  reported,
  g = 1,
  m = 1,
  algorithm = "SS",
  n_starts = 1,
  max_start_attempts = 1,
  max_iter = 50,
  seed = 3
)
summary(fit)
```

For externally assembled reports, provide the complete rule through
`metadata$reporting_design`. Missing or inconsistent design metadata does not
invalidate the fit, but information-derived fields are returned as `NA` with a
reason. A finite interval-valued report is supported by the likelihood, while
its Fisher-information contribution is not implemented in the first release.
